Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance

### 2024-04-18 paper/paper.qmd
Added more libraries

library(tidyverse)
library(palmerpenguins)
library(here) 
library(knitr)
library(janitor)
library(arrow)
library(here)
library(gridExtra)
library(gtsummary)
library(modelsummary)

>>>>

library(palmerpenguins)
library(here) 
library(arrow)
library(here)
library(gridExtra)
library(gtsummary)

library(boot)
library(broom.mixed)
library(collapse)
library(dataverse)
library(gutenbergr)
library(janitor)
library(knitr)
library(marginaleffects)
library(modelsummary)
library(rstanarm)
library(tidybayes)
library(tidyverse)
